Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-07-15 STAT-paper-template/APA/fertile.Rnw
fixed non-reproducible path
switched from sweave to knitr

<<fertile, message = FALSE>>=
library(fertile)
search()
file.exists("~/Desktop/my_data.csv")
read.csv("~/Desktop/my_data.csv")
@

@@

<<setwd, message=FALSE>>=
setwd("~/Desktop")
@

@@

<<set-project>>=
proj_dir <- "~/Dropbox/git/baumer-lab/fertile/tests/testthat/project_miceps"
@

>>>>

<<fertile, message = FALSE, error = TRUE>>=
library(fertile)
search()
file.exists("~/Desktop/my_data.csv")
read.csv("~/Desktop/my_data.csv")
@

@@

<<setwd, message=FALSE, error = TRUE>>=
setwd("~/Desktop")
@

@@

<<set-project>>=
proj_dir <- "project_miceps"
@
